---
title: "Third_tidytue"
author: "liujian"
date: "`r Sys.time()`"
output: 
  html_document:
    keep_md: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction 

**[Github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-06-11)**

# Packages and browsing

```{r libraries}
library(tidyverse)
library(gganimate)
library(lubridate)
meteorites <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv")

```
```{r glimpse}
glimpse(meteorites)

sapply(meteorites, function(x) length(unique(x)))

sapply(meteorites, range, na.rm = T)



```

# Clean the country name

```{r eda}

meteorites %>% 
  group_by(year) %>% 
  count() %>% 
  arrange(desc(n))
max(meteorites$mass, na.rm = T)

library(ggmap)
us <- map_data("state")

meteorites %>% 
  mutate()
  ggplot(aes(lat, long, size = mass)) +
  geom_point() +
  labs(title = 'Week: {current_frame}') +
  transition_manual(year) 
rr <- USArrests %>% 
  add_rownames("region") %>% 
  mutate(region=tolower(region))

 ggplot()+
   geom_map(data=us, map=us,
           aes(x=long, y=lat, map_id=region)) +
   labs(x=NULL, y=NULL)+
   coord_map()

```


# An interactive map shows which country has the top number of reviews

**Probably indicates these countries have a large population that are living on instant ramen if there are high numbers of reviews.**

```{r leaflet}

#https://stackoverflow.com/questions/33041266/r-rworldmap-map-issue-and-leaflet-application
world <- map("world", fill=TRUE, plot=FALSE)
world_map <- map2SpatialPolygons(world, sub(":.*$", "", world$names))
world_map <- SpatialPolygonsDataFrame(world_map,
                                      data.frame(country=names(world_map), 
                                                 stringsAsFactors=FALSE), 
                                      FALSE)

